Supervised Reinforcement Learning with Partial States: \\ a Teaching Method for Action Selection for HRI

### 2017-07-26 paper.tex
Update on Overleaf.

\author{Emmanuel Senft \\
CRNS \\
Plymouth University \\
United Kingdom\\
\And S\'{e}verin Lemaignan\\
CRNS \\
Plymouth University \\
United Kingdom\\
\And Paul Baxter\\
L-CAS\\
University of Lincoln\\
United Kingdom\\
 \And Tony Belpaeme\\
 CRNS\\ Plymouth University (UK) \\ iMinds \\ Ghent University (Be)}

\maketitle
\begin{abstract}
%As robots will integrate human society, they will have to satify humans'
%expectations. However at the design time, it seems hardly possible to
%know in advance exactly all the behaviours expected from the robot. As such to
%be accepted in human society robots have to learn how to interact with humans.
    Learning social interactions is a complex task that robots will have to
    master before being accepted in society. However, as no simulator of human
    interactions sufficiently
    precise exists today, the learning have to be made online and in the real
    world. Actions executed by the robot have impacts on humans, and as such
    have to be carefully selected, making the reliance on random exploration not
    applicable. Additionally, no clear reward function exists for
    social interactions. This implies that classical approaches such as
    Reinforcement Learning cannot be directly applied for learning how to
    interact with humans. As such we argue that
    robots will highly profit from human expertise and guidance to learn social
    interactions. And as the quantity of input a human can provide is limited,
    new methods have to be designed to use more efficiently human inputs. We
    combine the Supervised Progressively Autonomous Robot Competencies (SPARC)
    allowing a safer online learning with Reinforcement Learning and use
    partial states rather than full states to accelerate generalisation and
    obtain more quickly a usable action policy.
\end{abstract}
%===============================================================================

@@

Human-Robot Interaction (HRI) aims at having humans and robot living together
in the society, interacting socially in many different environments and
contexts. Robot are expected to behave appropriately regardless of the domain
of interaction. However, not all behaviours can be known in advance and be
implemented in the robot before its deployment in the real world. Similarly to
 humans, robots need
to be able to learn new tasks, new actions policies, new social norms and how
to make sense of the world surrounding them as they are interacting in the world.

For a robot, interacting in the real world requires to combine inputs
 from many sensors to create a space composed of large number dimensions and
select actions appropriated to the current space. However,
 parts of the state can be irrelevant to the current goal or current state and
 are not required
 to be taken into account to select the current action, only a limited number of
 features in the space are important. To interact efficiently, a robot has to
 learn to identify these features and associate them to related actions.

@@

In previous work~\cite{senft2015sparc,senft2017supervised}, we introduced the
Supervised Progressively Autonomous Robot Competencies (SPARC), a way to
teach a robot an action policy while interacting based on a supervisor
correcting actions about to be executed by the robot. In this paper, we propose
to extend this approach to allow the supervisor to highlight features in the
environment associated to the selected action. During the action selection
phase, the robot can compare these features, defined as partial states, with the
current state to select an action based on which previously identified
features are currently in the environment and submit it to its supervisor.

@@

The main framework for an agent to learn how to interact in an environment while
interacting is Reinforcement 
Learning (RL)~\cite{kober2013reinforcement,sutton1998reinforcement}. In RL, an
agent is interacting in an environment
providing numerical reward in reaction to the agent's actions and
the agent learns an action policy to maximise the expected cummulative discounted
reward received.

%Classic approaches in RL generally rely on exploring virtual environments where the agent
%tries to maximise the reward.
In many cases where RL achieves success, the agent
has access to a virtual environment where the only real cost of exploring is 
time and energy, and the agent can interact as long as needed to gather
enough information on the environment to find a correct action policy. When
these conditions are reunited, RL can achieve impressive results, as shown by
the victory of a computer in Backgammon back in the
90s~\cite{tesauro1995temporal} or more recently the success mastering the game
of go~\cite{silver2016mastering}. Even where a virtual environment is available,
but especially when it is not, human knowledge is required at many steps of the
design of the algorithm or the learning phase to achieve an efficient action
policy.

@@

\subsubsection{Design decisions:}
Initial knowledge has to be use in the designing of the algorithm, the
representation of the state and actions spaces and the reward funtion. For
example, only carefully crafted features allowed
Tesauro to improve its algorithm for Backgammon from a intermediate-level player
to super-human level~\cite{tesauro1995temporal}. Similarly, the design of
complex neural networks for state generalisation, the representation of actions
as motor primitives rather than raw motor angles or adding additional
information in the reward function have important impacts on the ability of
the robot to reach a successful policy~\cite{kober2013reinforcement}.

\subsubsection{Demonstrations:}
Initial knowledge can be provided to the agent learning through demonstrations.
These demonstrations can be used to create an initial policy sufficiently
efficient to start interacting in the environment and gather information to
improve over time. This initial policy, required to receive meaningful feedback
from the environment can be impossible to reach by relying only on random
exploration and feedback from the environment. For example the game of Go in its larger board
size contains more than $10^{210}$ states, so exhaustive search is not possible.
Authors of \cite{silver2016mastering} started with
supervised learning from go masters' games to learn a decent policy and then
used deep learning, self play and tree search to achieve super-human
capabilities and beating human best players.

These demonstrations can also be used to learn a reward function. With Inverse
Reinforcement Learning, the agent is not provided with a reward function, but
derives it from a set of expert demonstrations. The agent can then explore
around the demonstrated policy to optimise the reward function. With
this approach, Abbeel and Ng achieved better than human control for a robotic
helicopter~\cite{abbeel2004apprenticeship} based on demonstrations from experts
and further exploration and autonomous learning.

\subsubsection{Guiding the learning:}
Rather than solely providing initial knowledge
to the agents, humans can also guide the agent throughout the learning in a more
human-like teaching manner.

A first approach consists in sequencing the tasks the robot will face. 
This approach, known as "scaffolding" \cite{saunders2006teaching}, progressively
increases the difficulty and complexity of the task as the robot is learning
reaching policies not directly learnable in the final environment.

Approaches from animal conditioning have also been transfered to Machine Learning. 
For example, the TAMER framework~\cite{knox2009interactively} is an adaptation of "shaping",
tuning an animal's behaviour by providing rewards to guide it to the desired
behaviour. Unlike other RL setups, with TAMER, the
reward is not provided by the environment but by a human observer. With this
approach the teacher can adapt the 
rewards to the current policy and performance of the agent, for example starting to reward
positively suboptimal behaviours but better than the current policy and
later, as the agent improve its behaviour, reward these same suboptimal
behaviours negatively and only the optimal ones positively.

Another approach to guide the the learning is to bias the action selection.
In~\cite{thomaz2008teachable}, the authors propose to use a human supervisor to
supply  an agent both rewards and potential guidance or advise indicating where
the agent should pay attention, or what it should do next. They show that
giving the power to the supervisor to bias the action selection can improve the
learning, making it faster and safer.

In \cite{senft2015sparc}, we introduced the Supervised Progressively
Autonomous Robot Competencies (SPARC). SPARC relies on a supervisor with the
ability to control the robot's actions. This teacher is presented with the
actions the robot is about to execute and can cancel an action about to be
executed, let it be
executed or select another to be executed. Based on the supervisor's decisions,
the robot learns which actions are desired and can refine its policy over time
reducing the need for the teacher to correct or select an action.

SPARC gives control on the robot actions to an expert, who can guide the
exploration in the desired part of the environment which ensures the robot's
behaviour is consistently appropriate. As the exploration is
guided, and all the actions are useful, the learning can be faster than
autonomous learning or feedback based learning as illustrated in Figure
\ref{fig:comparison}.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{./fig/motivation.pdf}
    \caption{Idealised expectation for performance, autonomy and human workload for a
    an autonomous learner, an approach using human rewards and SPARC.}
    \label{fig:comparison}
\end{figure}

@@

In \cite{senft2017supervised}, we presented a way to combine SPARC and RL, by
assigning a positive reward to every action executed by the robot as it would
have been explicitely or implicitely approved by the supervisor. However this method
was  directly mapping a single (state, action) pair to a reward without making
use of any kind of generalisation, it was not applicable to
environments with a continuous or high dimensional space or undeterministic
transition from one state to another, such as interactions with humans.

@@

To make RL applicable in high dimensional or continuous states, the algorithm
requires a way to generalise knowledge to unseen states. 
A classical approach is to use a first layer of neural
network or to use deep reinforcement learning relying on deep neural
networks to learn a mapping state action Qvalue for example. 
These approaches, neural network based, relies on having a large number of
datapoints to converge toward a good function approximator. However, 
 in many application, especially in HRI, these amounts of data are not
obtainable due to time or unconsistency of human reactions, so methods to
generalise with a lower number of inputs are required.

@@

In this paper we propose to use a human to highlight the relevant features of
the environment to reduce the state dimension of the points only to relevant
information.
We introduce the concept of partial state, a sliced version of the state defined
only on a subset of the dimensions of the state. This shifts the (state, action)
pair paradigm to (partial state, action)  
and in the case of RL, the tuple (state, action, reward) to (partial state,
action, reward). This allows to compare the current state and the
datapoints only on relevant features for action selection.

@@

When the agent execute an action $a$ in state $s$, it receives the reward $r$
associated with the partial state $s'$. For example, a state $s$ could be
defined in 4 dimensions such as ${s=[1,0.2,0,0.5]}$, and $s'$ in two dimensions with
${s'=[-,0.2,0,-]}$ with symbol '$-$' reprensenting the dimensions removed. For
the learning algorithm, this means that the action $a$ has been evaluated $r$ in
the partial state $s'$.

@@

    \caption{Algorithm for selecting an action based on previous
    partial state action rewards tuples and current state.}
    \label{algo}
\end{algorithm}

@@

When selecting an action with following Algorithm~\ref{algo}, the agent can also use
the dimensions of the close state $s'$ used for the selection to indicate the
supervisor which parts of the state have been used for the action selection.

@@

SPARC has been showed to be compatible with RL in \cite{senft2017supervised},
and can also be easily combined with the approach presented in this paper using
partial states. For example, when selecting an action for the robot to be
executed, the supervisor can also select which features in the environment
should be selected in the partial state, and this associates the reward +1
to this action in this partial state. Similarly when an action is
proposed to the supervisor the features represented by the dimensions of the
closest partial state can be exposed to the supervisor as a way to explain why
this action has been selected. Facing this, the supervisor can: not react,
letting the action being executed and associating a reward of +1 to the partial
state and the action proposed, change the partial state to correct the features
related to this action or cancel it, preventing the execution and associating a
reward of -1 to the partial state identified by the robot or the supervisor.

\section{Example of application}

An example of application yet to be tested is robot for teaching children.
A robot can play an educative game with children to teach them notions about
diverse topics according to the needs of the teacher. For this example, a child
and a robot are playing a game about food web, teaching wich animals eat which
ones on a Sandtray~\cite{baxter2012touchscreen} as shown in
Figure~\ref{fig:game}. In addition to the child and
the robot, an adult supervises the robot using a tablet with a Graphical User
Interface (GUI) (Figure~\ref{fig:gui}) to teach the robot how to interact with the child.
\begin{figure}
        \centering
  \includegraphics[width=80mm]{./fig/game.png} 
    \caption{Game displayed on the Sandtray the child is playing with the robot.}
        \label{fig:game}
\end{figure}

@@

In the current implementation, the state is defined by the distance between each
animals and their life. With these features selected, the partial state
transmitted to the user is the distance between the eagle and the rat, the eagle's life and
the rat's life. Similarly, when selecting an action, the supervisor can 
select features in the state relevant to the selection.

The main limitations of the approach reside in the difference of
representation of the state and action spaces between the supervisor and the
algorithm and the limit in communication. For example a user could try to move
an animal close to another one,
and depending of the representation of the actions on the algorithm side, the
action might not be understood in the same way. Similarly, features used by the
supervisor to select actions might not be represented in the state used by the
algorithm. And lastly, in the case of implicit selection of features, a single
case of features representation (for example highlighting two animals) might not
be perceived in the same way by observers.

@@

The current work could also be extended to allow the agent continue to improve its
behaviour even in the absence of a supervisor, progressively exploring around the
learnt policy improving its behaviour beyond the demonstrations. This
could be done by allowing the supervisor to provide rewards during the learning
phase and combine these rewards with the demonstrations to learn a reward
function in a fashion similar to Inverse Reinforcement Learning
\cite{abbeel2004apprenticeship} or TAMER \cite{knox2009interactively}. This
could also use partial states associated to these rewards to ease the
generalisation of the reward function with only a low number of datapoints.
But without the supervisor, the assumption that only a
myopic action selection is sufficient would not hold anymore and the problem of
delayed rewards would have to be tackled.
%===============================================================================
%\section{Conclusion}
%\label{sec:conclusion}
%==============================================================================
\section{Acknowledgments}
This work was supported by the EU FP7 DREAM project (grant no.  611391) and EU
H2020 Marie Sklodowska-Curie Actions project DoRoThy (grant 657227).

>>>>

\author{Emmanuel Senft \\
CRNS \\
Plymouth University \\
United Kingdom\\
\And S\'{e}verin Lemaignan\\
CRNS \\
Plymouth University \\
United Kingdom\\
\And Paul Baxter\\
L-CAS\\
University of Lincoln\\
United Kingdom\\
 \And Tony Belpaeme\\
 CRNS\\ Plymouth University (UK) \\ ID Lab -- imec \\ Ghent University (BE)}

\maketitle
\begin{abstract}
%As robots will integrate human society, they will have to satify humans'
%expectations. However at the design time, it seems hardly possible to
%know in advance exactly all the behaviours expected from the robot. As such to
%be accepted in human society robots have to learn how to interact with humans.
    Social interacting is a complex task for which machine learrning holds particular promise. However, as no sufficiently
    accurate simulator of human interactions exists today, the learning of social interaction strategies has to happen online in the real
    world. Actions executed by the robot impact on humans, and as such
    have to be carefully selected, making it impossible to rely on random exploration. Additionally, no clear reward function exists for
    social interactions. This implies that classical approaches such as
    Reinforcement Learning cannot be directly applied for learning how to
    interact with the social world. As such we argue that
    robots will profit from human expertise and guidance to learn social
    interactions. And as the quantity of input a human can provide is limited,
    new methods have to be designed to use human input more efficiently. In this paper we describe a setpu in which We
    combine a framework called Supervised Progressively Autonomous Robot Competencies (SPARC), which
    allows safer online learning with Reinforcement Learning, with the use
    partial states rather than full states to accelerate generalisation and
    obtain more quickly a usable action policy.
\end{abstract}
%===============================================================================

@@

Human-Robot Interaction (HRI) studies how people and robot can co-exist in society, and how they can interact socially in different environments and
contexts. Robot are expected to behave appropriately regardless of the domain
of interaction. However, it is impossible to foresee all possible interaction outcomes in dynamic and open social domains, as such the robot's responses cannot be implemented in the robot before its deployment in the real world. Similar to
how people learn, robots need to be able to learn how to complete tasks through learning and optimising action policies. This including learning social norms and how to make sense of the social world.

For a robot, interacting in the real world often requires taking in a diverse and large range of sensory inputs, which results in a high-dimensional sensory space. The robots then is required to select actions based on its current state in sensor space. However,
 parts of the state can be irrelevant to the current goal, and
 as such should not be taken into account when selecting the current action. Often, only a limited number of
 features in the space are important. To interact efficiently, a robot has to
 learn to identify these salient features and associate them with appropriate actions.

@@

In previous work~\cite{senft2015sparc,senft2017supervised}, we introduced the
Supervised Progressively Autonomous Robot Competencies (SPARC), a way to
teach a robot an action policy while interacting based on a human supervisor
intervening and correcting actions before they were executed by the robot. In this paper, we propose
to extend this approach to allow the supervisor to highlight features in the
environment relevant for the selected action. During the action selection
phase, the robot can compare these features, defined as partial states, with the
current state to select an action. The selected is presented to the human supervisor, who can either correct the action or approve it for execution.

@@

The main framework for an agent to learn how to interact in an environment while
interacting is Reinforcement 
Learning (RL)~\cite{kober2013reinforcement,sutton1998reinforcement}. In RL, an
agent interacting in an environment
receives numerical rewards in reaction to its actions. The agent subsequently learns an action policy to maximise the expected cummulative discounted reward.

%Classic approaches in RL generally rely on exploring virtual environments where the agent
%tries to maximise the reward.
In many cases where RL achieves success, the agent
has access to a virtual environment where the only real cost of exploring is 
computational effort: the agent can interact as long as needed to gather
enough information on the environment and the result of its actions on the environment in order to find a sufficiently optimal action policy. Using simulation RL can achieve impressive results, as shown in RL learning to play Backgammon in the
90s~\cite{tesauro1995temporal} to the more recent success in mastering the game
of Go~\cite{silver2016mastering}. Even when a virtual environment is available,
but especially when it is not, human knowledge and effort is required during the
design of the algorithm or the learning phase before the learning can be successful.

@@

\subsubsection{Design decisions:}
Initial knowledge has to be use in the design of the algorithm, the
representation of the state and actions spaces and the reward funtion. For
example, only carefully crafted features allowed
Tesauro to improve its algorithm for Backgammon from a intermediate-level player
to super-human level~\cite{tesauro1995temporal}. Similarly, the design of
complex neural networks for state generalisation, the representation of actions
as motor primitives rather than raw motor angles or adding additional
information in the reward function have important impacts on the ability of
the robot to reach a successful policy~\cite{kober2013reinforcement}.

\subsubsection{Demonstrations:}
Initial knowledge can be provided to the agent through demonstrations.
These demonstrations can be used to create an initial policy which is sufficiently
efficient to start interacting in the environment and gather information to
improve over time. This initial policy, required to receive meaningful feedback
from the environment can be impossible to reach by relying only on random
exploration and feedback from the environment. For example the game of Go in its larger board
size contains more than $10^{210}$ states, so exhaustive search is not possible.
Silver et al. \cite{silver2016mastering} started with
supervised learning from Go masters' games to learn a decent enough policy and then
proceeded using deep learning, self play and tree search to achieve super-human
capabilities and beating the best human players.

These demonstrations can also be used to learn a reward function. With Inverse
Reinforcement Learning, the agent is not provided with a reward function, but
derives it instead from a set of expert demonstrations. The agent can then explore
around the demonstrated policy to optimise the reward function. With
this approach, Abbeel and Ng achieved better than human control for a robotic
helicopter~\cite{abbeel2004apprenticeship} based on demonstrations from experts
and further exploration and autonomous learning.

\subsubsection{Guiding the learning:}
Rather than solely providing initial knowledge
to the agents, humans can also guide the agent during its learning, a method more resembling human teaching.

A first approach consists in sequencing the tasks the robot will face. 
This approach, known as ``scaffolding'' \cite{saunders2006teaching}, progressively
increases the difficulty and complexity of the task as the robot is learning
to reach policies which would take prohibitively long without scaffolding.

Approaches from animal conditioning have also been transfered to Machine Learning. 
For example, the TAMER framework~\cite{knox2009interactively} is an adaptation of ``shaping'',
tuning an animal's behaviour by providing rewards to guide it to the desired
behaviour. Unlike other RL setups, with TAMER, the
reward is not provided by the environment but by a human observer. With this
approach the teacher can adapt the 
rewards to the current policy and performance of the agent, for example starting to positively reward
 suboptimal behaviours that are better than the current policy and
later, as the agent improves its behaviour, reward these same suboptimal
behaviours negatively and only the optimal ones positively.

Another approach to guide the learning is to bias the action selection.
In~\cite{thomaz2008teachable}, the authors propose to use a human supervisor to
supply an agent with both rewards and potential guidance indicating what
the agent should pay attention to, or what action it should take next. They show that
giving the power to the supervisor to bias the action selection can improve the
learning, making it faster and safer.

In \cite{senft2015sparc}, we introduced the Supervised Progressively
Autonomous Robot Competencies (SPARC). SPARC relies on a supervisor with the
ability to control the robot's actions. This supervisor is presented with the
action the robot is about to execute. He can then choose to cancel it, allow it to be
executed, or can select an alternative action. Based on the supervisor's decisions,
the robot learns which actions are desired and can as such refine its policy over time
reducing the need for the supervisor to correct or select an action.

SPARC gives control of the robot's actions to an expert, who can guide the
exploration in the desired part of the environment which ensures the robot's
behaviour is consistently appropriate. As the exploration is
guided, and all the actions are useful, the learning can be faster than
autonomous learning or feedback based learning as illustrated in Figure
\ref{fig:comparison}.

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{./fig/motivation.pdf}
    \caption{An illustration of the evoluation over time of the performance, autonomy and human workload for a
    an autonomous learner, an approach using human rewards, and SPARC.}
    \label{fig:comparison}
\end{figure}

@@

In \cite{senft2017supervised}, we presented a way to combine SPARC and RL, by
assigning a positive reward to every action executed by the robot, making the assumption that every action has been explicitely or implicitely approved by the supervisor. However this method
was  directly mapping a single (state, action) pair to a reward without making
use of any kind of generalisation. As such it was not applicable to
environments with a continuous or high dimensional space or non-deterministic
transitions from one state to another, elements which are typically present in social interactions.

@@

To make RL applicable in high dimensional or continuous states, the algorithm
requires a way to generalise knowledge to unseen states. 
A classic approach is to use a feed-forward neural
network or to use deep reinforcement learning relying on deep neural
networks to learn a the value function. 
These approaches rely on having a large number of
datapoints to converge toward a good function approximator. However, 
 in many applications and especially in HRI, these amounts of data are not
available or obtainable due to practical constraints. Furthermore, human responses are often noisy and lack consistency, so methods are needed which can generalise from a low number of noise data points.

@@

In this paper we propose to use a human user to highlight the relevant features of
the environment to reduce the state dimension of the points only to relevant
information.
We introduce the concept of a partial state, a sliced version of the state defined
only on a subset of the dimensions of the state. This shifts the (state, action)
pair paradigm to (partial state, action)  
and in the case of RL, the tuple (state, action, reward) to (partial state,
action, reward). This allows to compare the current state and the
datapoints only on relevant features for action selection.

@@

When the agent executes an action $a$ in state $s$, it receives the reward $r$
associated with the partial state $s'$. For example, a state $s$ could be
defined in 4 dimensions such as ${s=[1,0.2,0,0.5]}$, and $s'$ in two dimensions with
${s'=[-,0.2,0,-]}$ with symbol '$-$' reprensenting the dimensions removed. For
the learning algorithm, this means that the action $a$ has been evaluated $r$ in
the partial state $s'$.

@@

    \caption{Algorithm for selecting an action based on the previous
    (partial state, action, reward) tuples and the current state.}
    \label{algo}
\end{algorithm}

@@

When selecting an action, the agent can also use
the dimensions of the close state $s'$ used for the selection to indicate the
supervisor which parts of the state have been used for the action selection.

@@

SPARC has been shown to be compatible with RL in \cite{senft2017supervised},
and can also be easily combined with the approach presented in this paper using
partial states. For example, when selecting an action for the robot to be
executed, the supervisor can also select which features in the environment
should be selected as the partial state, and this associates the reward 
to this action in this partial state. Similarly, when an action is
proposed to the supervisor the features represented by the dimensions of the
closest partial state can be exposed to the supervisor as a way to explain why
this action has been selected. Facing this, the supervisor can: (1) not react,
allowing the action to be executed and associating a reward of +1 to the partial
state and the action proposed, (2) change the partial state to correct the features
related to this action or (3) cancel it, preventing the execution and associating a
reward of -1 to the partial state identified by the robot or the supervisor.

\section{Application scenario}

An example of an application is a social robot which interacts with children in an educational scenario.
The robot plays an educational game with children to teach them notions about
diverse topics according to the needs of the teacher. For this example, a child
and a robot are playing a game about the food web, teaching wich animals eat which
ones on a Sandtray~\cite{baxter2012touchscreen} as shown in
Figure~\ref{fig:game}. In addition to the child and
the robot, an adult supervises the robot using a tablet with a Graphical User
Interface (GUI) (Figure~\ref{fig:gui}) to teach the robot how to interact with the child.
\begin{figure}
        \centering
  \includegraphics[width=80mm]{./fig/game.png} 
    \caption{Game displayed on the Sandtray the child is playing with the robot.}
        \label{fig:game}
\end{figure}

@@

In the current implementation, the state is defined by the distance between each
animal and their life. With these features selected, the partial state
transmitted to the user is the distance between the eagle and the rat, the eagle's life and
the rat's life. Similarly, when selecting an action, the supervisor can 
select features in the state relevant to the action.

The main limitations of the approach reside in the difference of
representation of the state and action spaces between the supervisor and the
algorithm and the limit in communication. For example a user could try to move
an animal close to another one,
and depending on the representation of the actions on the algorithm side, the
action might not be understood in the same way. Similarly, features used by the
supervisor to select actions might not be represented in the state used by the
algorithm. And lastly, in the case of implicit selection of features, a single
case of features representation (for example highlighting two animals) might not
be perceived in the same way by observers.

@@

The current work could also be extended to allow the agent to continue to improve its
behaviour even in the absence of a supervisor, progressively exploring around the
learnt policy improving its behaviour beyond the demonstrations. This
could be done by allowing the supervisor to provide rewards during the learning
phase and combine these rewards with the demonstrations to learn a reward
function in a fashion similar to Inverse Reinforcement Learning
\cite{abbeel2004apprenticeship} or TAMER \cite{knox2009interactively}. This
could also use partial states associated to these rewards to ease the
generalisation of the reward function with only a low number of datapoints.
But without the supervisor, the assumption that only a
myopic action selection is sufficient would not hold anymore and the problem of
delayed rewards would have to be tackled.
%===============================================================================
%\section{Conclusion}
%\label{sec:conclusion}
%==============================================================================
\section{Acknowledgments}
This work was supported by the EU FP7 DREAM project (grant no.  611391) and EU
H2020 Marie Sklodowska-Curie Actions project DoRoThy (grant 657227).
